Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-04 phd/dissertation/chapter3.tex
Finished cf case

TODO:

\begin{thm}
  Let $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.
  Then $\pl F \codewin PF_{F,C}(\kappa)$.
\end{thm}

\begin{thm}
  Let $\kappa$ be the limit of cardinals $\kappa_n$ such that
  $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$.
  Then $F \codewin \pfgame{\kappa}$.
\end{thm}

>>>>

We aim to show that $\pl F \codewin \pfgame\kappa$ for all
$\kappa$.

\begin{thm}
  Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
  Then $\pl F \codewin PF_{F,C}(\kappa)$.
\end{thm}

\begin{proof}
Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
$W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
$W\subseteq c(\gamma_W)$.

Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
$W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.

Define the coding strategy $\sigma$ as follows:
  \[
    \sigma(\emptyset) = \emptyset
  \]
  \[
    \sigma(\<N,W\>)
      =
    N
      \cup
    (|N|+1)
      \cup
    \{\gamma_W\}
      \cup
    \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
  \]

Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
$N_0=\sigma(\emptyset)$, and
$N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
playthrough of the game coresponding to the coding strategy $\sigma$ and
attack $a$.

Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
$n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
that $\alpha\in c(\gamma_{W_i})\rest n$.
Finally, we consider
  \[
    N_{n+1}
      =
    \sigma(\<N_n,W_n\>)
      \supseteq
    \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
      \supseteq
    c(\gamma_{W_i})\rest |N_n|
  \]
and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
\end{proof}

\begin{thm}
  Let $\kappa$ be the limit of cardinals $\kappa_n$ such that
  $\cf{[\kappa_n]^{\leq\omega}}=\kappa_n$.
  Then $F \codewin \pfgame{\kappa}$.
\end{thm}
